Log Journal Project Theme 9

### 2022-11-02 Paper.Rmd
FInished the paper

---
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(knitr)
library(kableExtra)
library(pander)
library(ggplot2)
library(gridExtra)
library(ggpmisc)
library(ggpubr)
library(ggridges)
library(ggfortify)
```
# Result

@@

```{r}
attr_names <- c("seq.name", "mcg", "gvh", "alm", "mit", "erl",
                "pox", "vac","nuc", "loc.site" )
data_types <- c("str", "double", "double", "double", "double", "double",
                "logical", "double", "double", "factor")
data_labels <- c("Accession number for the SWISS-PROT database",
                 "McGeoch's method for signal sequence recognition",
                 "von Heijne's method for signal sequence recognition",
                 "Score of the ALOM membrane spanning region prediction program",
                 "Score of discriminant analysis of the amino 
                 acid content of the N-terminal region",
                 "Presence of 'HDEL' substring",
                 "Peroxisomal targeting signal in the C-terminus",
                 "Score of discriminant analysis of the amino acid content 
                 of vacuolar and extracellular proteins",
                 "Score of discriminant analysis of nuclear 
                 localization signals of nuclear and non-nuclear proteins",
                 "The class is the localization site")
codebook <- data.frame(Name=attr_names, 
                       Fullname=data_labels, 
                       Datatypes=data_types)
kbl(codebook, booktabs = T, align = "c") %>%
  kable_styling(full_width = T) %>%
  column_spec(2, width = "10cm")
```

\begin{center}
\emph{Table 1:} The codebook.
\end{center}

The last column is the sequence's localization site. There are ten different possibilities for this. Yeast proteins were classified into ten classes: **cytoplasmic:** cytoskeletal (CYT); nuc]ear (NUC); vacuolar (VAC); mitochondrial (MIT); isomal (POX); **extracellular:** including those localized against the cell wall (EXC); proteins localized to the lumen of the endoplasmic reticulum (ERL); membrane proteins with a cleaved signal (ME1); membrane proteins with an uncleared signal (ME2); and membrane proteins with no N-terminal sign (ME3), where ME1, ME2,and ME3 proteins may be localized to the plasma membrane, the endoplasmic reticulum membrane, or the membrane of a golgi body.

@@

```{r}
abbrv <- c("CYT", "NUC", "MIT", "ME3", "ME2", "ME1", "EXC", "VAC", "POX", "ERL")
loc.fullname <- c("cytosolic or cytoskeletal", "nuclear", "mitochondrial", "membrane protein, no N-terminal signal", "membrane protein, uncleaved signal", "membrane protein, cleaved signal", "extracellular", "vacuolar", "peroxisomal", "endoplasmic reticulum lumen")
amount <- c(463, 429, 244, 163, 51, 44, 37, 30, 20, 5)
pander(data.frame(Abbreviation=abbrv, 
                  Fullname=loc.fullname, 
                  Amount=amount))
```

\begin{center}
\emph{Table 2:} Sequence localization sites.
\end{center}

There are alot of CYT and NUC localizations. ERL localization is the least. There are only five of these in the dataset.

@@

```{r}
data <- as_tibble(read.table("yeast.data", sep = ""))
colnames(data) <- attr_names
pander(head(data))
```

\begin{center}
\emph{Table 3:} First six rows of the dataset.
\end{center}

As seen from the table, the loaded dataset. It has a char datatype for the first and last column. And every other column has a double datatype.

@@

```{r, fig.cap="A waffle chart of the categorical composition", fig.width=6, fig.height=3}
df <- expand.grid(y = 1:28, x = 1:53)
categ_table <- sort(table(data$loc.site), decreasing = T)
df$category <- factor(rep(names(categ_table), categ_table))
ggplot(df, aes(x = x, y = y, fill = category)) +
geom_tile(color = "black", size = 0.5) +
scale_x_continuous(expand = c(0, 0)) +
scale_y_continuous(expand = c(0, 0), trans = 'reverse') +
scale_fill_brewer(palette = "Set3") +
labs(title="Waffle Chart", subtitle="'Class' of localization") +
xlab(NULL) + ylab(NULL)
```

Figure 1 shows the number of each classification of the dataset. There are alot of CYT and NUC localization. And there are only `r nrow(subset(data, loc.site=="ERL", loc.site))` of ERL.

## Clean the data

@@

```{r}
data <- data[, -1]
pander(head(data))
```

\begin{center}
\emph{Table 4:} First six rows of the dataset with the first column dropped.
\end{center}

As stated on the website there are `r sum(is.na(data))` missing values.

```{r}
data$loc.site <- as.factor(data$loc.site)
str(data$loc.site)
```

The data type of the column loc.site has been successfully changed to factors.

The ERL column has changed. from a double to a logical datatype. As seen in figure 2 below, only numbers 1 and 0.5 appear, but for a logical datatype you need 1 and 0. All 0.5 have been changed to 0.

@@

```{r, warning=FALSE, message=FALSE, fig.cap="ERL column data distrubution", fig.width=10, fig.height=4}
my_list <- as.data.frame(table(data[,"erl"]))
names(my_list) <- c("Values", "Freq")
ggplot(data, mapping = aes(x = "", y = erl)) + geom_violin(alpha=0.2) + geom_jitter(width = 0.5, alpha = 0.25, height = 0.005, color = "red") + xlab(NULL) + annotate(geom = "table", x = 0.5, y = 0.75, label = list(my_list)) + ylim(0, 1) + labs(title="ERL Variable", subtitle="Data distrubution")
```

```{r}
data$erl[data$erl == 0.5] <- 0
data$erl <- as.logical(data$erl)
m <- sapply(data, typeof)
m[m=="integer"] <- "factor"
pander(m)
```

\begin{center}
\emph{Table 5:} Each column name and the typeof the datatype.
\end{center}

Each column has been changed so that it has the right data type.

## Exploratory data analysis

```{r}
table <- summary(data[, -c(5,9)])
panderOptions('table.continues', '')
pander(table)
```

\begin{center}
\emph{Table 6:} Summary of the dataset.
\end{center}

As observed in table 6 the data has already been transformed with a min-max normalisation. All the datapoints are between 0 and 1. Mcg and gvh are normally distributed. Alm and mit are skewed, but nothing too crazy to be worried about. Vac and nuc are really skewed. However, it's not yet bad enough to worry about it. Pox is very oddly distributed.

@@

```{r, fig.cap="Closer look at the pox variable", fig.width=10, fig.height=4}
my_list <- as.data.frame(table(data[,"pox"]))
names(my_list) <- c("Values", "Freq")
p1 <- ggplot(data, mapping = aes(x = "", y = pox)) + geom_violin(alpha=0.2) + 
  geom_jitter(width = 0.5, alpha = 0.25, height = 0.005, color = "red") + xlab(NULL)
p1 + annotate(geom = "table", x = 0.5, y = 0.75, label = list(my_list)) + labs(title="Pox Variable", subtitle="Data distrubution")
```

Almost all the data points are 0. This could cause problems later on. Since more than 95% of all the data points are 0.

```{r, fig.cap="Frequency plot of pox variablee", fig.height=3}
d <- as.data.frame(table(subset(data, pox > 0, select=loc.site)))
ggplot(d, aes(Var1, Freq)) +
  geom_linerange(
    aes(x = Var1, ymin = 0, ymax = Freq), 
    color = "lightgray", size = 1.5
    )+
  geom_point(aes(color = Var1), size = 2) + labs(title="Frequency plot of pox variable", x="localization site", y = "Count")
```

If the pox value is not zero then the classification is Pox, Mit or Cyt. This means that Pox has a high probability when the Pox value is not zero.

With a heatmap, you can easily see where there are correlations between variables.

```{r}
cor_matrix <- cor(data[, -c(5,9)])
cor_matrix <- as_tibble(cor_matrix)
cor_matrix <- cor_matrix %>% mutate(varnames = all_of(attr_names)[-c(1,6,10)])
kbl(cor_matrix, booktabs = T, align = "c") %>%
  kable_styling(full_width = T)
```

\begin{center}
\emph{Table 7:} The calculated correlation matrix.
\end{center}

This has been transformed into a long matrix.

```{r}
cor_matrix_long <- pivot_longer(data = cor_matrix, 
                                 cols = all_of(attr_names)[-c(1,6,10)], 
                                 names_to = "variable", values_to = "cor")
pander(head(cor_matrix_long))
```

\begin{center}
\emph{Table 8:} The long calculated correlation matrix.
\end{center}

```{r, fig.cap="A heatmap pairwise correlation of selected numeric variables", fig.height=4}

ggplot(data = cor_matrix_long, aes(x=varnames, y=variable, fill=cor)) + 
    geom_tile() + 
    labs(x=NULL, y=NULL, title="Heatmap Correlation") + 
    scale_fill_gradient(high = "purple", low = "white" )
```

As seen from the heatmap, there is some correlation between mcg and gvh. Pox, on the other hand, has almost no correlation with any other variable.

There needs to be data correlation with the classes. The height of the peak doesn’t matter much, shifted peaks do.

```{r, warning=FALSE, message=FALSE, fig.cap="Ridge line plot between mcg and gvh"}
p1 <- ggplot(data, aes(x=mcg, y=loc.site, fill = loc.site)) + 
  geom_density_ridges2(rel_min_height = 0.005) + theme_minimal() + 
  coord_cartesian(clip = "off")
p2 <- ggplot(data, aes(x=gvh, y=loc.site, fill = loc.site)) + 
  geom_density_ridges2(rel_min_height = 0.005) + theme_minimal() + 
  coord_cartesian(clip = "off")
plot <- ggarrange(p1, p2, common.legend = TRUE)
annotate_figure(plot, top = text_grob("Ridge line plot", face = "bold", size = 14))
```

There are shifted peaks. This shows the distribution of the different classes.

A 1-way ANOVA test was carried out on the data.

```{r}
# Perform a one way anova test
res.aov <- summary(aov(mcg ~ loc.site, data = data))
p.value <- res.aov[[1]]$`Pr(>F)`[1]
```

The P-value: `r p.value` is < 0.05. So there is a significant difference.

@@

```{r, fig.cap="Classical (Metric) Multidimensional Scaling", fig.width=4, fig.height=2.5}
matrix <- with(data, rbind(mcg, gvh, alm, mit, pox, vac, nuc))
distmat <- dist(matrix)
autoplot(cmdscale(distmat, eig = TRUE), shape = FALSE, label = TRUE, label.size = 4)
```

As found in the heatmap, Mcg and Gvh are clustered. Vac and Alm are somewhat clustered; they are close to each other. Nuc, Mit and Pox are all on their own.

```{r, fig.cap="PCA plot", fig.width=6, fig.height=3}
df <- data[-c(5,9)]

pca_res <- prcomp(df, scale. = TRUE)

autoplot(pca_res, data = data, colour = 'loc.site', loadings = TRUE, loadings.label = TRUE)
```

Mcg and Gvh are also clustered in this PCA plot. As such, in contrast with the MDS plot, Vac and Alm are not clustered at all. Pox is in the centre.

@@

# Discussion & Conclusion

@@

@@

>>>>

---
output:
  pdf_document: 
    pandoc_args: --highlight=breezedark
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(ggpubr)
library(pander)
library(ggbiplot)
library(reshape2)
library(ggfortify)
library(ggalt)
library(ggridges)
library(cluster)
```

<!-- Copyright (c) 2022 John Busker. -->

<!-- Licensed under GPLv3. See gpl.md -->

# Cellular Localization Prediction

## Can the cellular localization Sites of proteins be predicted using probabilistic classification.

![<https://www.hj9l.com/zhidao/changshi/13854.html>](Resources/images/cover.jpg)

```{=tex}
\vspace*{\fill}
\begin{flushright}
John Busker\\
352905\\
Bio-Informatics\\
Dave Langers, and Bart Barnard\\
28-10-2022
\end{flushright}
```
\newpage

# Table of Contents

1. [Introduction](#introduction) \dotfill 3

2. [Materials and Methods](#materials-and-methods) \dotfill 4  
3. [Results](#results) \dotfill 5  
  3.1 [Codebook](#codebook) \dotfill 5  
  3.2 [Machine Learning](#machine-learning) \dotfill 8

4. [Discussion and Conclusion](#discussion-and-conclusion) \dotfill 12  
  4.1 [Discussion](#discussion) \dotfill 12  
  4.2 [Conclusion](#conclusion) \dotfill 12

5. [References](#references) \dotfill 13

# Introduction

Protein activities and their subcellular locations in cells are strongly connected. Finding proteins' positions within cells is frequently the initial step in understanding them, and their sites serve as a model for medication design. The amino acid sequence of a protein mostly determines where it will localize within a cell. Using this knowledge, a software has been developed to define a simple model of classification of yeast localization in cells. The efficient arrangement of biological data into databases and the creation of algorithms, such string algorithms, to manipulate that data, have largely defined the area of computational biology. The dataset consists of 1484 yeast sequences from SWISS-PROT using the annotations from YPD.

Research question: Can the cellular localization Sites of proteins be predicted using probabilistic classification.

# Materials and Methods

The data has been retrieved from [uci.](https://archive.ics.uci.edu/ml/datasets/Yeast) The dataset consists of 1484 yeast sequences from SWISS-PROT using the annotations from YPD. In this section, we are going to talk about the results we found from the dataset.

Yeast proteins were classified into ten classes: **cytoplasmic:** cytoskeletal (CYT); nuc]ear (NUC); vacuolar (VAC); mitochondrial (MIT); isomal (POX); **extracellular:** including those localized against the cell wall (EXC); proteins localized to the lumen of the endoplasmic reticulum (ERL); membrane proteins with a cleaved signal (ME1); membrane proteins with an uncleared signal (ME2); and membrane proteins with no N-terminal sign (ME3), where ME1, ME2,and ME3 proteins may be localized to the plasma membrane, the endoplasmic reticulum membrane, or the membrane of a golgi body.

Eight features were used in classification. Here below are all the features

-   **mcg**: McGeoch's method for signal sequence recognition.\
-   **gvh**: von Heijne's method for signal sequence recognition.\
-   **alm**: Score of the ALOM membrane spanning region prediction program.\
-   **mit**: Score of discriminant analysis of the amino acid content of the N-terminal region (20 residues long) of mitochondrial and non-mitochondrial proteins.\
-   **erl**: Presence of "HDEL" substring (thought to act as a signal for retention in the endoplasmic reticulum lumen). Binary attribute.\
-   **pox**: Peroxisomal targeting signal in the C-terminus.\
-   **vac**: Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins.\
-   **nuc**: Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins.

It is always important to look at the data and to look at the quality of the data. No proper conclusion can be drawn from low quality data. For recurrent errors the data can be corrected. The data needs to be modified to make sure the data gets the highest quality to perform the analysis on. This is achieved by performing exploratory data analysis on the dataset. Modifying and removing parts of the dataset to get best. A RandomForest classifier has been chosen for the classification of the unknown instances. The parameters has been optimized for usability and speed. See the [logjournal](https://github.com/AlfonsoJan/Theme9).

A java application has been developed. The software using Weka carried out the calculations required to carry out the probabilistic inference. The application can quickly classify new instances given from a file on from the command line. See the [repo](https://bitbucket.org/janalfonso/wekawrapper/) for the code.

# Results

@@

```{r, echo=FALSE}
attr_names <- c("seq.name", "mcg", "gvh", "alm", "mit", "erl",
                "pox", "vac","nuc", "loc.site" )
data_types <- c("str", "double", "double", "double", "double", "double",
                "logical", "double", "double", "factor")
data_labels <- c("Accession number for the SWISS-PROT database",
                 "McGeoch's method for signal sequence recognition",
                 "von Heijne's method for signal sequence recognition",
                 "Score of the ALOM membrane spanning region prediction program",
                 "Score of discriminant analysis of the amino 
                 acid content of the N-terminal region",
                 "Presence of 'HDEL' substring",
                 "Peroxisomal targeting signal in the C-terminus",
                 "Score of discriminant analysis of the amino acid content 
                 of vacuolar and extracellular proteins",
                 "Score of discriminant analysis of nuclear 
                 localization signals of nuclear and non-nuclear proteins",
                 "The class is the localization site")
codebook <- data.frame(Name=attr_names, 
                       Fullname=data_labels, 
                       Datatypes=data_types)
kbl(codebook, booktabs = T, align = "c") %>%
  kable_styling(full_width = T) %>%
  column_spec(2, width = "10cm")
```

```{=tex}
\begin{center}
\emph{Table 1:} The codebook.
\end{center}
```
The last column is the sequence's localization site. There are ten different possibilities for this. Yeast proteins were classified into ten classes: **cytoplasmic:** CYT; NUC; VAC; MIT; POX; **extracellular:** EXC; ERL; ME1; ME2; ME3.

@@

```{r, echo=FALSE}
abbrv <- c("CYT", "NUC", "MIT", "ME3", "ME2", "ME1", "EXC", "VAC", "POX", "ERL")
loc.fullname <- c("cytosolic or cytoskeletal", "nuclear", "mitochondrial", "membrane protein, no N-terminal signal", "membrane protein, uncleaved signal", "membrane protein, cleaved signal", "extracellular", "vacuolar", "peroxisomal", "endoplasmic reticulum lumen")
amount <- c(463, 429, 244, 163, 51, 44, 37, 30, 20, 5)
pander(data.frame(Abbreviation=abbrv, 
                  Fullname=loc.fullname, 
                  Amount=amount))
```

```{=tex}
\begin{center}
\emph{Table 2:} Sequence localization sites.
\end{center}
```
There are alot of CYT and NUC localizations. ERL localization is the least. There are only five of these in the dataset.

@@

```{r, echo=FALSE}
data <- as_tibble(read.table("Resources/yeast.data", sep = ""))
colnames(data) <- attr_names
pander(head(data))
```

```{=tex}
\begin{center}
\emph{Table 3:} First six rows of the dataset.
\end{center}
```
As seen from the table, the loaded dataset. It has a char datatype for the first and last column. And every other column has a double datatype.

@@

```{r, fig.cap="A waffle chart of the categorical composition", fig.width=6, fig.height=3, echo=FALSE}
df <- expand.grid(y = 1:28, x = 1:53)
categ_table <- sort(table(data$loc.site), decreasing = T)
df$category <- factor(rep(names(categ_table), categ_table))
ggplot(df, aes(x = x, y = y, fill = category)) +
geom_tile(color = "black", size = 0.5) +
scale_x_continuous(expand = c(0, 0)) +
scale_y_continuous(expand = c(0, 0), trans = 'reverse') +
scale_fill_brewer(palette = "Set3") +
labs(title="Waffle Chart", subtitle="'Class' of localization") +
xlab(NULL) + ylab(NULL)
```

Figure 2 shows the number of each classification of the dataset. There are alot of CYT and NUC localization. And there are only `r nrow(subset(data, loc.site=="ERL", loc.site))` of ERL.

@@

```{r, echo=FALSE}
data <- data[, -1]
pander(head(data))
```

```{=tex}
\begin{center}
\emph{Table 4:} First six rows of the dataset with the first column dropped.
\end{center}
```
As stated on the website there are `r sum(is.na(data))` missing values. This has been confirmed using R.

```{r, echo=FALSE}
data$loc.site <- as.factor(data$loc.site)
```

It can be more convenient to have a variable in a factor form instead of numeric form. The data type of the column loc.site has been successfully changed to factors.

The ERL column has changed. from a double to a logical datatype. As seen in table 5 below, only numbers 1 and 0.5 appear, but for a logical datatype you need 1 and 0. All 0.5 have been changed to 0.

```{r, echo=FALSE}
pander(table(data$erl))
```

```{=tex}
\begin{center}
\emph{Table 5:} A table showing distrubtion of the ERL column.
\end{center}
```
```{r, echo=FALSE}
data$erl[data$erl == 0.5] <- 0
data$erl <- as.logical(data$erl)
m <- sapply(data, typeof)
m[m=="integer"] <- "factor"
pander(m)
```

```{=tex}
\begin{center}
\emph{Table 6:} Each column name and the typeof the datatype.
\end{center}
```
Each column has been changed so that it has the right data type.

At pox, vac and nuc, you don't see shifted peaks. At mcg and gvh you really see shifted peaks this shows a distribution of the different classes. There are small shifted peaks at alm en mit, this shows that there is difference but not so much.

@@

```{r, warning=FALSE, message=FALSE, fig.cap="Ridge line plot between mcg and gvh", echo=FALSE, fig.width=6, fig.height=6}
p1 <- ggplot(data, aes(x=mcg, y=loc.site, fill = loc.site)) + 
  geom_density_ridges2(rel_min_height = 0.005) + theme_minimal() + 
  coord_cartesian(clip = "off")
p2 <- ggplot(data, aes(x=gvh, y=loc.site, fill = loc.site)) + 
  geom_density_ridges2(rel_min_height = 0.005) + theme_minimal() + 
  coord_cartesian(clip = "off")
plot <- ggarrange(p1, p2, common.legend = TRUE)
annotate_figure(plot, top = text_grob("Ridge line plot", face = "bold", size = 14))
```

Now you can really see that the peaks are shifted.

We need to test the data to see if there is significant difference between it. Using a 1-way ANOVA test.

```{r, echo=FALSE}
# Perform a one way anova test
res.aov <- summary(aov(mcg ~ loc.site, data = data))
p.value <- res.aov[[1]]$`Pr(>F)`[1]
```

The P-value is `r p.value` \< 0.05. So there is a significant difference.

## Machine Learning

Weka was used to test which algorithm is the best to use for the classification of instances. An accurate algorithm is needed that accurately predicts the dataset. It needs a high percentage of correct classifications on the dataset. An algorithm needs to be fast for the best usage. What if there is a dataset of 1 million observations. And it should also not contain too many false negatives and false positives.

Using the experiment of Weka testing has been done on every representatives of all classifier categories. And ZeroR and OneR for a baseline performance. Decision Trees (C4.5, J48, RandomForest), Nearest Neighbor (IBk), SVM (SMO), NaiveBayes (Naïve Bayes) and Linear Logistic (SimpleLogistic). And carried out classifications 10-fold cross validation. The result were saved in a .csv file.

```{r, echo=FALSE}
weka.result <- read.table("Resources/Result.csv", header = TRUE, sep = ",")
# Remove weka.classifiers.* from classifier name
for (i in 1:length(weka.result$Key_Scheme)) {
  name <- weka.result$Key_Scheme[i]
  tweaked.name <- strsplit(name, split = ".", fixed = TRUE)[[1]][4]
  weka.result$Key_Scheme[i] <- tweaked.name
}
```

```{r,fig.cap="Area under the curve for different classifiers", echo=FALSE}
res <- aggregate(Area_under_ROC ~ Key_Scheme, data = weka.result, mean)
ggplot(data=res, aes(x=Key_Scheme, y=Area_under_ROC, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  labs(x="Classifier", y="Area under curve (ROC)", 
       title="Area under the curve for different classifiers") + 
  geom_hline(aes(yintercept=min(Area_under_ROC)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(Area_under_ROC)), linetype = 'dashed') + 
  geom_text(aes(label=round(Area_under_ROC, digits=2)), vjust=1.5, size=3.5)
```

An integrated measurement of a measurably effect or phenomena is the area under the curve. A higher Area under the curve the better. RandomForest has the highest area under the curve, while OneR has the lowest with 0.49 and ZeroR with a close second last with 0.5.

The algorithm also needs te be precise.

@@

```{r, fig.cap="Average precisionfor different classifiers", echo=FALSE}
res <- aggregate(IR_precision ~ Key_Scheme, data = weka.result, mean)

ggplot(data=res, aes(x=Key_Scheme, y=IR_precision, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + 
  labs(x="Classifier", y="Precision", 
       title="Average precision for different classifiers") + 
  geom_hline(aes(yintercept=min(IR_precision)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(IR_precision)), linetype = 'dashed') + 
  geom_text(aes(label=round(IR_precision, digits=2)), vjust=1.5, size=3.5)

```

RandomForest also has the highest average precision with 0.66. And OneR has the lowest with 0.04. ZeroR is not in this plots because it only consist of NaN.

Several algorithms cannot make a prediction for the classification VAC (0.000) and for some they get an error (?). 1 algorithm IBk has a very low prediction for VAC. All the algorithm above in the figure except for ZeroR, OneR, SMO and SimpleLogistic were used in the Weka Experimenter to compare.

![Ranking of chosen algorithms](%22Resources/images/WekaSD.png%22)

RandomForest has a 'v' next to their result. This means that the difference in the accuracy for these algorithms compared to all the other algorithms is significant. And RandomForest beat all 4 algorithms.

The classification of VAC seems to be the most concerning of all. It has been removed and tested against not removed. To see if there is an significant difference.

@@

![Removed class difference](%22Resources/images/WekaDataEdit.png%22)

There is no significant difference between removing VAC and keeping VAC.

Weka will find the optimal parameters for a classifier. With CVParameterSelection in Weka were the best parameters found.

```{r, echo=FALSE}
attr <- c("P", "I", "num-slots", "K", "M", "V", "S")
attr.descr <- c("Size of each bag, as a percentage of the training set size.", 
                "Number of iterations.", "Number of execution slots.", 
                "Number of attributes to randomly investigate.", 
                "Number of attributes to randomly investigate.", 
                "Set minimum numeric class variance proportion.", 
                "Seed for random number generator.")
old.val <- c(100, 100, 1, 0, 1, 0.001, 1)
new.val <- c(50, 1000, 0, 1, 1, 0.001, 1)
pander(data.frame(Attribute=attr, Description=attr.descr, Old.Values=old.val, New.Values=new.val))
```

```{=tex}
\begin{center}
\emph{Table 7:} Each parameter with the old and new best value if necessary.
\end{center}
```
This table shows the parameters with their default settings and their new. P, I, num-slots and K were different than the default settings. The build will take more time because it does 10 times more I(terations).

![Iterations ranked]("Resources/images/WekaIterRank.png")

Number 1 in the figure above is with 1000 I(terations) and number 2 is 100 I(terations). And there is not a significant difference.

@@

# Discussion and Conclusion

@@

Only 8 classifiers had been used. From our research, we found that RandomForest is the best, however, perhaps another untested classifier is much better than RandomForest. Only the removal of VAC was considered what if much better precision and classification would have run if another classifier had been removed.

@@

1484 yeast proteins were classified into 10 classes with an accuracy of 61%.

# References
